---
title: "Class 12_AD616"
author: "Yusen Zhou"
date: "2023-05-03"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(fitdistrplus)
library(extraDistr)
library(MASS)
```

Patient Dataset: https://healthdata.gov/Hospital/COVID-19-Reported-Patient-Impact-and-Hospital-Capa/anag-cw7u 

PPE Daily Demand: https://www.ahrmm.org/aspr-tracie-hospital-personal-protective-equipment-planning-tool 

Masks  = 1/patient/day + 6 + 4
Gowns  = 1/patient/day + 6 + 4
Gloves = 4/patient/day + 36 + 8 

PPE Lead Time: https://www.sciencedirect.com/science/article/pii/S2214716023000052 

Masks  = Triangular(1,4,1)
Gowns  = Uniform(4,7)
Gloves = Uniforms(2,4)

# MASSACHUSETTS GENERAL HOSPITAL 

## Patient Number in hospital simulator 

```{r}
df <- read_csv("COVID-19_Reported_Patient_Impact_and_Hospital_Capacity_by_Facility.csv")
dim(df)

MGH <- df %>% filter(state=="MA" & hospital_name=="MASSACHUSETTS GENERAL HOSPITAL")
MGH <- MGH %>% dplyr::select(hospital_name, collection_week, total_adult_patients_hospitalized_confirmed_covid_7_day_avg) %>% 
  na.omit() %>% 
  filter(total_adult_patients_hospitalized_confirmed_covid_7_day_avg > 0)
MGH <- MGH[order(MGH$collection_week, decreasing = F),]
colnames(MGH)[3] <- "covid_cases"
MGH$covid_cases <- ceiling(MGH$covid_cases)
dim(MGH)

ggplot(MGH, aes(x=covid_cases))+ geom_histogram(fill="cyan2",color="black")

fit_1 <- fitdist(MGH$covid_cases, "lnorm")
fit_2 <- fitdist(MGH$covid_cases, "nbinom")
fit_3 <- fitdist(MGH$covid_cases, "gamma")
gofstat(list(fit_1, fit_2, fit_3))
# Lognormal Distribution has the lowest KS statistic, so we'll use lognormal distribution to simulate our patient demand. 
fit_1$estimate    



sample_patient <- function(){
  rlnorm(1, 3.2381935, 0.6779113) %>% ceiling()
}

mask_lead <- function(){
  rtriang(1, a = 1, b = 4, c = 1) %>% ceiling()
}

gown_lead <- function(){
  runif(1, 4, 7) %>% ceiling()
}

glove_lead <- function(){
  runif(1, 2, 4) %>% ceiling()
}
```

# Inventory Control Simulation 

## Mask Simulation

**We want to minimize average inventory level**

**Service Level should be at least 95%**

```{r}
# est. avg. mask demand/day = 43
ceiling(mean(MGH$covid_cases)) + 6 + 4 

sim1 <- function(r_point, r_qty){
  v_inv_level <- c()
  v_satisfaction_rate <- c()
  # return average inventory level from simulations
  for(n in 1:50){        # simulate 50 times
    b_inv <- rep(0, 60)
    e_inv <- rep(0, 60)
    r_ind <- rep(0, 60)
    b_inv[1] <- 43*7    # b_inv is set to 7 days of avg inventory for Mask. 
    total_demands <- 0
    satisfied_demands <- 0
    for(i in 1:60){
      if(r_ind[i]==1){
        b_inv[i] <- b_inv[i] + r_qty
      }
      demand <- sample_patient()*1 + 6 + 4
      total_demands <- total_demands + demand
      # 1) b_inv[i]<demand --> we do not meet all demands --> e_inv[i] is 0
      # 2) b_inv[i]>=demand --> we meet all demands --> e_inv[i] is b_inv[i]-demand
      if(b_inv[i]<demand){
        e_inv[i] <- 0
        satisfied_demands <- satisfied_demands + b_inv[i]
      }
      else{
        e_inv[i] <- b_inv[i]-demand
        satisfied_demands <- satisfied_demands + demand
      }
      # reorder
      cond1 <- (e_inv[i] < r_point)
      cond2 <- sum(r_ind[(i+1):length(r_ind)], na.rm=T)==0
      if(cond1 & cond2){
        # reorder will be placed on day (i+1)
        lead <- mask_lead()
        # reorder will be delivered on day(i+1+lead)
        r_ind[i+1+lead] <- 1
      }
      b_inv[i+1] <- e_inv[i]
    }
    # average inventory level, service level
    a_inv_level <- mean(e_inv)
    satisfaction_rate <- satisfied_demands/total_demands
    v_inv_level <- c(v_inv_level, a_inv_level)
    v_satisfaction_rate <- c(v_satisfaction_rate, satisfaction_rate)
  }
  #plot(e_inv, type = "b")+abline(h=r_point)
  return(c(mean(v_inv_level), mean(v_satisfaction_rate)))
}
```


## Mask Optimization

```{r message=FALSE, warning=FALSE}
library(DEoptim)
```

```{r}
opt_func <- function(params){
  r_point <- params[1] %>% round()
  r_qty <- params[2] %>% round()
  res <- sim1(r_point, r_qty)
  if(res[2]<0.98)
    return(Inf)
  return(res[1])
}

set.seed(616)
opt_satisfaction_rate <- DEoptim(opt_func, lower = c(100,100), upper = c(1000,1000))  # Find the lowest inv_level, with the an service level cannot lower than 98%.  
opt_satisfaction_rate$optim 

sim1(202.5326, 181.4824)
```

### For Mask inventory management, the optimal reorder point is 203, and the optimal reorder quantity is 182 (rounded) 

## Gown Simulation 

```{r}
sim2 <- function(r_point, r_qty){
  v_inv_level <- c()
  v_satisfaction_rate <- c()
  for(n in 1:50){
    b_inv <- rep(0, 60)
    e_inv <- rep(0, 60)
    r_ind <- rep(0, 60)
    b_inv[1] <- 43*10     # b_inv is set to 10 days of avg inventory for Gown.  
    total_demands <- 0
    satisfied_demands <- 0
    for(i in 1:60){
      if(r_ind[i]==1){
        b_inv[i] <- b_inv[i] + r_qty
      }
      demand <- sample_patient()*1 + 6 + 4     # change to gown demand here
      total_demands <- total_demands + demand
      if(b_inv[i]<demand){
        e_inv[i] <- 0
        satisfied_demands <- satisfied_demands + b_inv[i]
      }
      else{
        e_inv[i] <- b_inv[i]-demand
        satisfied_demands <- satisfied_demands + demand
      }
      cond1 <- (e_inv[i] < r_point)
      cond2 <- sum(r_ind[(i+1):length(r_ind)], na.rm=T)==0
      if(cond1 & cond2){
        lead <- gown_lead()       # change to gown lead_time here
        r_ind[i+1+lead] <- 1
      }
      b_inv[i+1] <- e_inv[i]
    }
    a_inv_level <- mean(e_inv)
    satisfaction_rate <- satisfied_demands/total_demands
    v_inv_level <- c(v_inv_level, a_inv_level)
    v_satisfaction_rate <- c(v_satisfaction_rate, satisfaction_rate)
  }
  #plot(e_inv, type = "b")+abline(h=r_point)
  return(c(mean(v_inv_level), mean(v_satisfaction_rate)))
}
```

## Gown Optimization 

```{r}
opt_func <- function(params){
  r_point <- params[1] %>% round()
  r_qty <- params[2] %>% round()
  res <- sim2(r_point, r_qty)
  if(res[2]<0.98)
    return(Inf)
  return(res[1])
}

set.seed(616)
opt_satisfaction_rate <- DEoptim(opt_func, lower = c(100,100), upper = c(1000,1000))  # Find the lowest inv_level, with the an service level cannot lower than 98%.  
opt_satisfaction_rate$optim 

sim2(377.8645, 315.8100)
```

### For Gown inventory management, the optimal reorder point is 378, and the optimal reorder quantity is 316 (rounded) 



## Glove Simulation 

```{r}
sim3 <- function(r_point, r_qty){
  v_inv_level <- c()
  v_satisfaction_rate <- c()
  for(n in 1:50){
    b_inv <- rep(0, 60)
    e_inv <- rep(0, 60)
    r_ind <- rep(0, 60)
    b_inv[1] <- (33*4+36+8)*7     # b_inv is set to 7 days of avg inventory for Glove  
    total_demands <- 0
    satisfied_demands <- 0
    for(i in 1:60){
      if(r_ind[i]==1){
        b_inv[i] <- b_inv[i] + r_qty
      }
      demand <- sample_patient()*4 + 36 + 8     # change to Glove demand here
      total_demands <- total_demands + demand
      if(b_inv[i]<demand){
        e_inv[i] <- 0
        satisfied_demands <- satisfied_demands + b_inv[i]
      }
      else{
        e_inv[i] <- b_inv[i]-demand
        satisfied_demands <- satisfied_demands + demand
      }
      cond1 <- (e_inv[i] < r_point)
      cond2 <- sum(r_ind[(i+1):length(r_ind)], na.rm=T)==0
      if(cond1 & cond2){
        lead <- glove_lead()       # change to gown lead_time here
        r_ind[i+1+lead] <- 1
      }
      b_inv[i+1] <- e_inv[i]
    }
    a_inv_level <- mean(e_inv)
    satisfaction_rate <- satisfied_demands/total_demands
    v_inv_level <- c(v_inv_level, a_inv_level)
    v_satisfaction_rate <- c(v_satisfaction_rate, satisfaction_rate)
  }
  #plot(e_inv, type = "b")+abline(h=r_point)
  return(c(mean(v_inv_level), mean(v_satisfaction_rate)))
}
```

## Glove Optimization 

```{r}
opt_func <- function(params){
  r_point <- params[1] %>% round()
  r_qty <- params[2] %>% round()
  res <- sim3(r_point, r_qty)
  if(res[2]<0.98)
    return(Inf)
  return(res[1])
}

set.seed(616)
opt_satisfaction_rate <- DEoptim(opt_func, lower = c(700,700), upper = c(2000,2000))  # Find the lowest inv_level, with the an service level cannot lower than 98%.  
opt_satisfaction_rate$optim 

sim3(988.1699, 846.5179)
```

### For Glove inventory management, the optimal reorder point is 989, and the optimal reorder quantity is 847. (rounded) 

